\bf Eye Fitting Straight Lines in the Modern Era

### 2022-02-07 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
finalized first round edits.

Much of the research on the perception of visual features in charts has been conducted in psychophysics and tests for accuracy and quantitative comparisons when understanding a plot. 
Cleveland and McGill conducted a series of cognitive tasks designed to establish a hierarchy of visual components for making comparisons [@cleveland1984graphical]. 
For example, it is more effective to display information on an $x$ or $y$ axis rather than using color in order to reduce the visual effort necessary to make numerical comparisons.
@cleveland1985graphical found that assessing the position of points along an axis is easier than determining the slope of a line. \svp{XXX we probably could include a few more papers and discussions here - the Cleveland 1984 and 1985 papers are based on the same study and are basically duplicates.}
The results of these cognitive tasks provide some consistent guidance for chart design; however, other methods of visual testing can further evaluate design choices and help us understand cognitive biases related to the evaluation of statistical charts.

@@

Initial studies in the 20th century explored the use of fitting lines by eye through a set of points [@finney1951subjective; @mosteller1981eye]. 
Common methods of fitting trends by eye involved maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. Recently, @ciccione2021can conducted a comprehensive set of studies investigating human ability to detect trends in graphical representations \svp{using these types of manipulations.} \ear{XXX this study was conducted online, but asked users to use the arrows on their keyboard to adjust the slope or select whether the shown slope was positive or negative}.

@@

In @ciccione2021can, participants were asked to judge trends, estimate slopes, and conduct extrapolation.
To estimate slopes, participants were asked to report the slope of the best-fitting regression line using a track-pad to adjust the tilt of a line on screen.
Results indicated the slopes participants reported were always in excess of the ideal slopes, both in the positive and in the negative direction, and those biases increase with noise and with number of points. 
This supports the results found in @mosteller1981eye and suggest that participants might use Deming regression when fitting a line to a noisy scatter-plot [@deming1943statistical; @linnet1998performance; @martin2000general] \ear{xxx added citation}.

While not explicitly intended for perceptual testing, in 2015, the New York Times introduced an interactive feature, called You Draw It [@aisch_cox_quealy_2015; @buchanan_park_pearce_2017; @katz_2017].
Readers are asked to input their own assumptions about various metrics and compare how these assumptions relate to reality.
The New York Times team utilizes Data Driven Documents (D3) [@bostock2011d3] \ear{xxx added citation} that allows readers to predict these metrics through the use of drawing a line on their computer screen with their computer mouse. 
After the reader has completed drawing the line, the actual observed values are revealed and the reader may check their estimated knowledge against the actual reported data.
While this interactive feature is designed to get readers to confront their own intuitions about data in the news, we feel that the interactivity of this method may be useful for another purpose.

@@

Participants were recruited through through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed 119 unique 'You Draw It' task plots; all completed you draw it task plots were included in the analysis. 
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a Shiny application [@shinyPkg] \ear{xxx added citation} found [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). \svp{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?} \ear{XXX linked to updated shinyapps.io through new repository - does not currently write data anywhere.}

@@

The intent of this research was to adapt 'You Draw It' from the New York Times feature as a tool and method for testing graphics and introduce a method for statistically modeling the participant drawn lines.
We provided support for the validity of the 'You Draw It' method by replicating the study found in @mosteller1981eye.
Using generalized additive mixed models, we assessed the deviation of the participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend, participants visually fit a regression line that mimics the first principle component regression as opposed to ordinary least squares regression. 
Data simulated with a larger variance provided strong support for a participants tendency to visually fit the first principle component regression.
Our results indicate that participants minimized the distance from the their regression line over both the $x$ and $y$ axis simultaneously. 
\svp{XXX some sentance that says that our results are much stronger than the original results because our analysis methods allow for more sophistication (and we have a slight technological advantage on the original paper's authors as well, after 40 years).}
These results provide support that humans perform "ensemble perception" in a statistical graphic setting.
We allowed participants to draw trend lines that deviated from a straight line and gained an insight into the curvature the human eye perceives in a set of points.

@@

\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/).
+ **\ear{RShiny Applet Code:}** \ear{The code used to create the RShiny Applet for data collection can be found} [\ear{here}](https://github.com/earobinson95/you-draw-it-validation-applet).

>>>>

Much of the research on the perception of visual features in charts has been conducted in psychophysics and tests for accuracy and quantitative comparisons when understanding a plot. 
Cleveland and McGill conducted a series of cognitive tasks designed to establish a hierarchy of visual components for making comparisons [@cleveland1984graphical]. 
For example, it is more effective to display information on an $x$ or $y$ axis rather than using color in order to reduce the visual effort necessary to make numerical comparisons.
@cleveland1985graphical found that assessing the position of points along an axis is easier than determining the slope of a line. \ear{Other studies focus on the viewers ability to perceive the strength of the relationship between $x$ and $y$ coordinates in a scatter-plot. For instance, when the data appear dense, viewers tend to overestimate the magnitude of the correlation coefficient} [@cleveland1982variables; @lauer1989density]. @cleveland1993visualizing. \ear{provides an argument for displaying cyclical patterns with an aspect ratio which sets the curve closet to 45$^{\circ}$.} @kosslyn2006graph \ear{examines how Gestalt principles of perceptual organization are instrumental in extracting data from a chart. For example, data points that are closer in space are more likely to be perceived as grouped} [@ciccione2020grouping]\ear{, and vertical and horizontal lines are easier to discriminate than oblique ones} [@appelle1972perception].
<!-- \svp{XXX we probably could include a few more papers and discussions here - the Cleveland 1984 and 1985 papers are based on the same study and are basically duplicates.} -->
The results of these cognitive tasks provide some consistent guidance for chart design; however, other methods of visual testing can further evaluate design choices and help us understand cognitive biases related to the evaluation of statistical charts.

@@

Initial studies in the 20th century explored the use of fitting lines by eye through a set of points [@finney1951subjective; @mosteller1981eye]. 
Common methods of fitting trends by eye involved maneuvering a string, black thread, or ruler until the fit is suitable, then drawing the line through the set of points. Recently, @ciccione2021can conducted a comprehensive set of studies investigating human ability to detect trends in graphical representations \ear{using manual adjustment and manipulation methods.}
<!-- \svp{using these types of manipulations.}  -->
<!-- \ear{XXX this study was conducted online, but asked users to use the arrows on their keyboard to adjust the slope or select whether the shown slope was positive or negative}. -->

@@

In @ciccione2021can, participants were asked to judge trends, estimate slopes, and conduct extrapolation.
To estimate slopes, participants were asked to report the slope of the best-fitting regression line using a track-pad to adjust the tilt of a line on screen.
Results indicated the slopes participants reported were always in excess of the ideal slopes, both in the positive and in the negative direction, and those biases increase with noise and with number of points. 
This supports the results found in @mosteller1981eye and suggest that participants might use Deming regression when fitting a line to a noisy scatter-plot [@deming1943statistical; @linnet1998performance; @martin2000general].

While not explicitly intended for perceptual testing, in 2015, the New York Times introduced an interactive feature, called You Draw It [@aisch_cox_quealy_2015; @buchanan_park_pearce_2017; @katz_2017].
Readers are asked to input their own assumptions about various metrics and compare how these assumptions relate to reality.
The New York Times team utilizes Data Driven Documents (D3) [@bostock2011d3] that allows readers to predict these metrics through the use of drawing a line on their computer screen with their computer mouse. 
After the reader has completed drawing the line, the actual observed values are revealed and the reader may check their estimated knowledge against the actual reported data.
While this interactive feature is designed to get readers to confront their own intuitions about data in the news, we feel that the interactivity of this method may be useful for another purpose.

@@

Participants were recruited through through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed 119 unique 'You Draw It' task plots; all completed you draw it task plots were included in the analysis. 
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a Shiny application [@shinyPkg] found [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). 
<!-- \svp{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?} \ear{XXX linked to updated shinyapps.io through new repository - does not currently write data anywhere.} -->

@@

The intent of this research was to adapt 'You Draw It' from the New York Times feature as a tool and method for testing graphics and introduce a method for statistically modeling the participant drawn lines.
We provided support for the validity of the 'You Draw It' method by replicating the study found in @mosteller1981eye.
Using generalized additive mixed models, we assessed the deviation of the participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend, participants visually fit a regression line that mimics the first principle component regression as opposed to ordinary least squares regression. 
Data simulated with a larger variance provided strong support for a participants tendency to visually fit the first principle component regression.
Our results indicate that participants minimized the distance from the their regression line over both the $x$ and $y$ axis simultaneously. 
\ear{We utilized modern technology to replicate a study conducted 40 years ago, and strengthend the original results with current analysis methods which allow for more flexibility and sophistication.}
<!-- \svp{XXX some sentance that says that our results are much stronger than the original results because our analysis methods allow for more sophistication (and we have a slight technological advantage on the original paper's authors as well, after 40 years).} -->
These results provide support that humans perform "ensemble perception" in a statistical graphic setting.
We allowed participants to draw trend lines that deviated from a straight line and gained an insight into the curvature the human eye perceives in a set of points.

@@

\newpage
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/).
+ **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found [here](https://github.com/earobinson95/you-draw-it-validation-applet).

### 2022-02-07 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
finalized first round edits.

Much of the research on the perception of visual features in charts has
been conducted in psychophysics and tests for accuracy and quantitative
comparisons when understanding a plot. Cleveland and McGill conducted a
series of cognitive tasks designed to establish a hierarchy of visual
components for making comparisons \citep{cleveland1984graphical}. For
example, it is more effective to display information on an \(x\) or
\(y\) axis rather than using color in order to reduce the visual effort
necessary to make numerical comparisons. \citet{cleveland1985graphical}
found that assessing the position of points along an axis is easier than
determining the slope of a line.
{\textcolor{blue}{The design choices we make can affect a viewers ability to judge relationships between $x$ and $y$ coordinates in a scatter plot. For instance, when the data appear dense, viewers tend to overestimate the magnitude of the correlation coefficient}}
\citep{cleveland1982variables, lauer1989density}.
\citet{cleveland1993visualizing}.
{\textcolor{blue}{provides an argument for displaying cyclical patterns with an aspect ratio which sets the curve closet to 45$^{\circ}$.}}

\begin{itemize}
\item
  {\textcolor{blue}{Gestalt principles of perceptual organization play a crucial role in data extraction [@kosslyn2006graph]: for example, data points that are closer in space are more likely to be perceived as grouped [@ciccione2020grouping], and vertical and horizontal lines are easier to discriminate than oblique ones [@appelle1972perception].}}
\end{itemize}

The results of these cognitive tasks provide some consistent guidance
for chart design; however, other methods of visual testing can further
evaluate design choices and help us understand cognitive biases related
to the evaluation of statistical charts.

@@

Initial studies in the 20th century explored the use of fitting lines by
eye through a set of points
\citep{finney1951subjective, mosteller1981eye}. Common methods of
fitting trends by eye involved maneuvering a string, black thread, or
ruler until the fit is suitable, then drawing the line through the set
of points. Recently, \citet{ciccione2021can} conducted a comprehensive
set of studies investigating human ability to detect trends in graphical
representations
{\textcolor{RedOrange}{using these types of manipulations.}}
{\textcolor{blue}{XXX this study was conducted online, but asked users to use the arrows on their keyboard to adjust the slope or select whether the shown slope was positive or negative}}.

@@

In \citet{ciccione2021can}, participants were asked to judge trends,
estimate slopes, and conduct extrapolation. To estimate slopes,
participants were asked to report the slope of the best-fitting
regression line using a track-pad to adjust the tilt of a line on
screen. Results indicated the slopes participants reported were always
in excess of the ideal slopes, both in the positive and in the negative
direction, and those biases increase with noise and with number of
points. This supports the results found in \citet{mosteller1981eye} and
suggest that participants might use Deming regression when fitting a
line to a noisy scatter-plot
\citep{deming1943statistical, linnet1998performance, martin2000general}
{\textcolor{blue}{xxx added citation}}.

While not explicitly intended for perceptual testing, in 2015, the New
York Times introduced an interactive feature, called You Draw It
\citep{aisch_cox_quealy_2015, buchanan_park_pearce_2017, katz_2017}.
Readers are asked to input their own assumptions about various metrics
and compare how these assumptions relate to reality. The New York Times
team utilizes Data Driven Documents (D3) \citep{bostock2011d3}
{\textcolor{blue}{xxx added citation}} that allows readers to predict
these metrics through the use of drawing a line on their computer screen
with their computer mouse. After the reader has completed drawing the
line, the actual observed values are revealed and the reader may check
their estimated knowledge against the actual reported data. While this
interactive feature is designed to get readers to confront their own
intuitions about data in the news, we feel that the interactivity of
this method may be useful for another purpose.

@@

Participants were recruited through through Twitter, Reddit, and direct
email in May 2021. A total of 35 individuals completed 119 unique `You
Draw It' task plots; all completed you draw it task plots were included
in the analysis. All participants had normal or corrected to normal
vision and signed an informed consent form. The experimental tasks took
approximately 15 minutes to complete. While this study does utilize a
convenience sample, as this is primarily a perceptual task, previous
results have found few differences between expert and non-expert
participants in this context \citep{vanderplas2015spatial}. These data
were collected to validate this method of graphical testing, with the
hopes of providing a new tool to assess graphical perception
interactively. Participants completed the experiment on their own
computers in an environment of their choosing. The experiment was
conducted and distributed through a Shiny application \citep{shinyPkg}
{\textcolor{blue}{xxx added citation}} found
\href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.
{\textcolor{RedOrange}{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?}}
{\textcolor{blue}{XXX linked to updated shinyapps.io through new repository - does not currently write data anywhere.}}

@@

The intent of this research was to adapt `You Draw It' from the New York
Times feature as a tool and method for testing graphics and introduce a
method for statistically modeling the participant drawn lines. We
provided support for the validity of the `You Draw It' method by
replicating the study found in \citet{mosteller1981eye}. Using
generalized additive mixed models, we assessed the deviation of the
participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend,
participants visually fit a regression line that mimics the first
principle component regression as opposed to ordinary least squares
regression. Data simulated with a larger variance provided strong
support for a participants tendency to visually fit the first principle
component regression. Our results indicate that participants minimized
the distance from the their regression line over both the \(x\) and
\(y\) axis simultaneously.
{\textcolor{RedOrange}{XXX some sentance that says that our results are much stronger than the original results because our analysis methods allow for more sophistication (and we have a slight technological advantage on the original paper's authors as well, after 40 years).}}
These results provide support that humans perform ``ensemble
perception'' in a statistical graphic setting. We allowed participants
to draw trend lines that deviated from a straight line and gained an
insight into the curvature the human eye perceives in a set of points.

@@

\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed
  \href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.
\item
  \textbf{{\textcolor{blue}{RShiny Applet Code:}}}
  {\textcolor{blue}{The code used to create the RShiny Applet for data collection can be found}}
  \href{https://github.com/earobinson95/you-draw-it-validation-applet}{{\textcolor{blue}{here}}}.
\end{itemize}

>>>>

Much of the research on the perception of visual features in charts has
been conducted in psychophysics and tests for accuracy and quantitative
comparisons when understanding a plot. Cleveland and McGill conducted a
series of cognitive tasks designed to establish a hierarchy of visual
components for making comparisons \citep{cleveland1984graphical}. For
example, it is more effective to display information on an \(x\) or
\(y\) axis rather than using color in order to reduce the visual effort
necessary to make numerical comparisons. \citet{cleveland1985graphical}
found that assessing the position of points along an axis is easier than
determining the slope of a line.
{\textcolor{blue}{Other studies focus on the viewers ability to perceive the strength of the relationship between $x$ and $y$ coordinates in a scatter-plot. For instance, when the data appear dense, viewers tend to overestimate the magnitude of the correlation coefficient}}
\citep{cleveland1982variables, lauer1989density}.
\citet{cleveland1993visualizing}.
{\textcolor{blue}{provides an argument for displaying cyclical patterns with an aspect ratio which sets the curve closet to 45$^{\circ}$.}}
\citet{kosslyn2006graph}
{\textcolor{blue}{examines how Gestalt principles of perceptual organization are instrumental in extracting data from a chart. For example, data points that are closer in space are more likely to be perceived as grouped}}
\citep{ciccione2020grouping}{\textcolor{blue}{, and vertical and horizontal lines are easier to discriminate than oblique ones}}
\citep{appelle1972perception}. The results of these cognitive tasks
provide some consistent guidance for chart design; however, other
methods of visual testing can further evaluate design choices and help
us understand cognitive biases related to the evaluation of statistical
charts.

@@

Initial studies in the 20th century explored the use of fitting lines by
eye through a set of points
\citep{finney1951subjective, mosteller1981eye}. Common methods of
fitting trends by eye involved maneuvering a string, black thread, or
ruler until the fit is suitable, then drawing the line through the set
of points. Recently, \citet{ciccione2021can} conducted a comprehensive
set of studies investigating human ability to detect trends in graphical
representations
{\textcolor{blue}{using manual adjustment and manipulation methods.}}

@@

In \citet{ciccione2021can}, participants were asked to judge trends,
estimate slopes, and conduct extrapolation. To estimate slopes,
participants were asked to report the slope of the best-fitting
regression line using a track-pad to adjust the tilt of a line on
screen. Results indicated the slopes participants reported were always
in excess of the ideal slopes, both in the positive and in the negative
direction, and those biases increase with noise and with number of
points. This supports the results found in \citet{mosteller1981eye} and
suggest that participants might use Deming regression when fitting a
line to a noisy scatter-plot
\citep{deming1943statistical, linnet1998performance, martin2000general}.

While not explicitly intended for perceptual testing, in 2015, the New
York Times introduced an interactive feature, called You Draw It
\citep{aisch_cox_quealy_2015, buchanan_park_pearce_2017, katz_2017}.
Readers are asked to input their own assumptions about various metrics
and compare how these assumptions relate to reality. The New York Times
team utilizes Data Driven Documents (D3) \citep{bostock2011d3} that
allows readers to predict these metrics through the use of drawing a
line on their computer screen with their computer mouse. After the
reader has completed drawing the line, the actual observed values are
revealed and the reader may check their estimated knowledge against the
actual reported data. While this interactive feature is designed to get
readers to confront their own intuitions about data in the news, we feel
that the interactivity of this method may be useful for another purpose.

@@

Participants were recruited through through Twitter, Reddit, and direct
email in May 2021. A total of 35 individuals completed 119 unique `You
Draw It' task plots; all completed you draw it task plots were included
in the analysis. All participants had normal or corrected to normal
vision and signed an informed consent form. The experimental tasks took
approximately 15 minutes to complete. While this study does utilize a
convenience sample, as this is primarily a perceptual task, previous
results have found few differences between expert and non-expert
participants in this context \citep{vanderplas2015spatial}. These data
were collected to validate this method of graphical testing, with the
hopes of providing a new tool to assess graphical perception
interactively. Participants completed the experiment on their own
computers in an environment of their choosing. The experiment was
conducted and distributed through a Shiny application \citep{shinyPkg}
found
\href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.

@@

The intent of this research was to adapt `You Draw It' from the New York
Times feature as a tool and method for testing graphics and introduce a
method for statistically modeling the participant drawn lines. We
provided support for the validity of the `You Draw It' method by
replicating the study found in \citet{mosteller1981eye}. Using
generalized additive mixed models, we assessed the deviation of the
participant drawn lines from the statistically fitted regression lines.
Our results found that when shown points following a linear trend,
participants visually fit a regression line that mimics the first
principle component regression as opposed to ordinary least squares
regression. Data simulated with a larger variance provided strong
support for a participants tendency to visually fit the first principle
component regression. Our results indicate that participants minimized
the distance from the their regression line over both the \(x\) and
\(y\) axis simultaneously.
{\textcolor{blue}{We utilized modern technology to replicate a study conducted 40 years ago, and strengthend the original results with current analysis methods which allow for more flexibility and sophistication.}}
These results provide support that humans perform ``ensemble
perception'' in a statistical graphic setting. We allowed participants
to draw trend lines that deviated from a straight line and gained an
insight into the curvature the human eye perceives in a set of points.

@@

\newpage
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed
  \href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.
\item
  \textbf{RShiny Applet Code:} The code used to create the RShiny Applet
  for data collection can be found
  \href{https://github.com/earobinson95/you-draw-it-validation-applet}{here}.
\end{itemize}
